How Important are Usage Examples in REST API Documentation?

### 2017-03-06 controlled_study.tex
legends are good now

\begin{tikzpicture}
    \begin{axis}[
        ybar,
        xtick=data,
        xticklabels from table={\groupone}{Task},
        legend style={at={(0.5,-0.15)},
        anchor=north,legend columns=-1},
        ylabel=Average Trial API Calls,
        title=Comparison of Trial vs. Successful API Calls,
        width=2.8in
    ]
    \addplot[pattern=crosshatch dots, pattern color=gray] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {groupone.csv};
    \addplot[draw=black] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {grouptwo.csv};
    \legend{G1: Using Original, G2: Using Forked}
    \end{axis}

    \begin{axis}[
      axis y line*=right,
      axis x line=none,
      ymin=0, ymax=100,
      ylabel= Success Rate,
      yticklabel={\pgfmathparse{\tick}\pgfmathprintnumber{\pgfmathresult}\%},
      width=2.8in
    ]
    \addplot[dashed,mark=*,gray] table [col sep=comma, x expr=\coordindex, y=SuccessRate] {groupone_success.csv};
    \addlegendentry{G1 Success Rate}

@@

>>>>

\begin{figure}

\begin{tikzpicture}
    \begin{axis}[
        ybar,
        xtick=data,
        xticklabels from table={\groupone}{Task},
        legend style={at={(0.5,-0.15)},
        anchor=north,legend columns=-1},
        ylabel=Average Trial API Calls,
        width=2.8in
    ]
    \addplot[pattern=crosshatch dots, pattern color=gray] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {groupone.csv};
    \addplot[draw=black] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {grouptwo.csv};
    \legend{G1: Using Original, G2: Using Forked}
    \end{axis}

    \begin{axis}[
      axis y line*=right,
      axis x line=none,
      ymin=0, ymax=100,
      ylabel= Success Rate,
      yticklabel={\pgfmathparse{\tick}\pgfmathprintnumber{\pgfmathresult}\%},
      width=2.8in,
      legend style={at={(1.0,1.25)},anchor=north east}
    ]
    \addplot[dashed,mark=*,gray] table [col sep=comma, x expr=\coordindex, y=SuccessRate] {groupone_success.csv};
    \addlegendentry{G1 Success Rate}

@@

\caption{DUMMY Comparison of Trial vs. Successful API Calls}
\end{figure}
